Using Camera Traps and Computer Vision to Quantify Wildlife Diversity and Co-Occurrence across \nOntario’s Far North

### 2023-03-03 analysis/paper/paper.qmd
improvements to text

<!-- The actual document text starts here:

## Summary

TBW

\newpage -->

@@

### Species ID summary

@@

### Ordination

TBW

```{r}
#| label: RDA-presence-absence
#| echo: false

@@

# Ordination
stopifnot(all(rownames(anns_wide_animals_table_tb)==rownames(extr_table_sub_tb)))

@@

### RDA based on events

```{r}
#| label: RDA-events
#| echo: false
events_tb_cam_hell <- vegan::decostand(events_tb_cam, "hellinger")

@@

# vegan::RsquareAdj(events_rda)
# custom_rda_plot(events_rda, sp_scale = 1.5, scale_x_sp=0.4, scale_y_sp=0.3,
#                 thres_plot = 0.3)
```

@@

```{r}
#| label: rda-clust
#| echo: false

@@

```{r}
#| label: map-groups
#| echo: false

@@

base_cut +
  ggplot2::geom_point(data = cams_sf_clust, cex = 1, shape=21, col="black",
                      ggplot2::aes(x=X, y=Y, fill=grp), 
                      inherit.aes = FALSE) +
  ggplot2::labs(fill="Group")
```

@@

```{r}
#| label: clust-geo-plot
#| echo: false

@@

### Density contourmaps

@@

```{r}
#| label: heatmap-facets
#| eval: false

@@

![alt text](../figures/Caribou_bplot.png "Caribou")
```{r}
#| label: heatmaps
#| echo: false

@@

```{r}
#| label: plot-tests
#| echo: false

# cams_sf_sp_sum %>%
#   dplyr::filter(species == "Caribou") %>%
#   ggplot2::ggplot() +
#   ggplot2::geom_raster(ggplot2::aes(x=X, y=Y, z=count)) +
#   ggplot2::facet_wrap(~month) +
#   ggplot2::coord_equal(xlim = c(-89, -84),
#                        ylim = c(50, 55))
```

>>>>

@@

### Community data

@@

### Ordination - presence-absence

@fig-rda-pa shows the triplot for the RDA on presence-absence data.

```{r}
#| label: fig-rda-pa
#| echo: false
#| fig-cap: "Triplot of RDA on presence-absence data"

@@

# Ordination
stopifnot(all(rownames(anns_wide_animals_table_tb)==
                rownames(extr_table_sub_tb)))

@@

### Ordination - relative abundances

@fig-rda-events shows the triplot for the RDA on relative abundance data.

```{r}
#| label: fig-rda-events
#| echo: false
#| fig-cap: "Triplot of RDA on relative abundance data"

events_tb_cam_hell <- vegan::decostand(events_tb_cam, "hellinger")

@@

# vegan::RsquareAdj(events_rda)
custom_rda_plot(events_rda, sp_scale = 1.5, scale_x_sp=0.4, scale_y_sp=0.3,
                thres_plot = 0.3)
```

@@

@fig-rda-events-clust shows the triplot for the RDA on relative abundance data,  with Ward clusters as ellipses.

```{r}
#| label: fig-rda-events-clust
#| echo: false
#| fig-cap: "Triplot of RDA on relative abundance data, with Ward clusters as ellipses"

@@

@fig-map-clust shows a map of clustered camera sites.

```{r}
#| label: fig-map-clust
#| echo: false
#| fig-cap: "Map of clustered camera sites"

@@

base_cut +
  ggplot2::geom_point(data = cams_sf_clust, cex = 1, shape=21, col="black",
                      ggplot2::aes(x=X, y=Y, fill=grp), 
                      inherit.aes = FALSE) +
  ggplot2::labs(fill="Group")
```
### Spatial clustering

@@

@fig-map-clust-geo shows a map of geographically constrained clustered camera sites.

```{r}
#| label: fig-map-clust-geo
#| echo: false
#| fig-cap: "Map of geographically constrained clustered camera sites"

@@

### Species heatmaps and bubbleplots

@@

```{r}
#| label: heatmap-facets
#| echo: false
#| eval: false

@@

![alt text](../figures/Caribou_bplot.png "Caribou")

```{r}
#| label: heatmaps
#| echo: false

@@
